---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSRjz0YGckkevoZyIPk5hvMtdQgQo3CvDLjm7PN4mZTiTBr25JHKWbcN4o33ZJZb4MPeHOzl4qzwje0/pub?output=csv")

latest_data <- logged_data %>% 
  rename(
    date = 1,
    ad_type = 2,
    times_seen = 3,
    brand = 4
  )

num_responses <- nrow(latest_data)
mean_seen <- mean(latest_data$times_seen)
max_seen <- max(latest_data$times_seen)
```

```{css}
/* Simple CSS styling */
h2 {
  color: #003366;
  border-bottom: 2px solid #003366;
  padding-bottom: 5px;
}
p {
  font-family: Arial, sans-serif;
  font-size: 16px;
  line-height: 1.5;
}
.plot-caption {
  font-style: italic;
  font-size: 14px;
}
```

## What kinds of ads are people seeing?

This report uses data from a Google Form where people recorded Instagram ads they saw, including the product type, brand, and how many times they saw it.

There were **`r num_responses`** responses.

On average, people saw each ad **`r round(mean_seen, 1)`** times — with the most frequently seen ad shown **`r max_seen`** times.

### Ad types: What products are most advertised?

```{r}
latest_data %>%
  ggplot() +
  geom_bar(aes(x = ad_type), fill = "#6495ED") +
  labs(title = "Number of Ads by Product Type",
       x = "Product Type",
       y = "Count",
       caption = "Source: Google Form Responses") +
  theme_minimal()
```

*This chart shows which types of products appeared most often in the reported ads.*

### Top brands: Who's advertising the most?

```{r}
latest_data %>%
  count(brand, sort = TRUE) %>%
  slice(1:10) %>%
  ggplot() +
  geom_bar(aes(x = reorder(brand, -n), y = n), stat = "identity", fill = "#FFA07A") +
  labs(title = "Top 10 Most Frequently Advertised Brands",
       x = "Brand",
       y = "Number of Mentions",
       caption = "Source: Google Form Responses") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

*These are the ten brands that appeared most frequently in the data.*
